
---
title: <span style="color:blue">"WeRateDogs Exploratory Data Analysis"</span>  
author: "Nawal YALA"
---    

<div style="text-align: justify;">  

> In this work I will present an analyse and vizualization of the tweet archive of Twitter user @dog_rates, also known as WeRateDogs. WeRateDogs is a Twitter account that rates people's dogs with a humorous comment about the dog. These ratings almost always have a denominator of 10. The numerators, though? Almost always greater than 10. 11/10, 12/10, 13/10, etc. Why? Because "they're good dogs Brent." WeRateDogs has over 4 million followers and has received international media coverage.
To more detail about this data, its structure and variables, please see the wrangling  process that I have done on it in the same directory.

```{r echo=FALSE , message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

library(ggplot2)
library(dplyr)
library(lubridate)
library(reshape2)
library(jpeg)
```

```{r echo=FALSE}

setwd('E:/NanoDegree/Wrangling/Projet')
rt <- read.csv('twitter_archive_master.csv')
```


<span style="color:blue">Overview on WeRateDogs tweet dataset and its structure </span> 

```{r echo=FALSE}
str(rt)
```

WeRateDogs dataset consists of 5922 observations and 17 variables.

```{r}
rt$jpg_url <- toString(rt$jpg_url)
```

# Univariate Plots Section

<span style="color:blue">Question: </span> What the most utility used by WeRateDogs to post tweets

```{r echo=FALSE}
ggplot( aes(x = source, y = ..prop.., group =1),  data = rt%>%filter(pred_algo =='algo1'))+
  geom_bar(color="steelblue", fill="white")+
    theme(aspect.ratio = 1/1)
```


<span style="color:blue">Question: </span>  How i the evolution of tweet number across year

```{r echo=FALSE}
# Add year column 
rt$year <- year(rt$timestamp)

```

```{r echo=FALSE}
ggplot(aes(x = year), data = rt%>%filter(pred_algo =='algo1'))+
  geom_bar(color="steelblue", fill="white")
```


Tweets are gathered  until August 1st, 2017. However we observe a 40% increase in tweets number in 2016 compared to 2015.


<span style="color:blue">Question: </span>  What is the most popular tweet?

First we get the max favorite_count / retweet_count

```{r echo=FALSE}
summary(rt$favorite_count)
```
Then we extract the tweet text and the dog image


```{r echo=FALSE}
text <- rt%>%filter( favorite_count == 164649, pred_algo =='algo1')%>%select(text)
jpg_url <- rt%>%filter( favorite_count == 164649, pred_algo =='algo1')%>%select(jpg_url)
```

```{r echo=FALSE}
text
```



```{r echo=FALSE}
jj <- readJPEG('popu.jpg',native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)
```



<span style="color:blue">Question: </span>  Which dog has the higher rating value?


```{r echo=FALSE}
summary(rt$Rating)
```


```{r echo=FALSE}
text <- rt%>%filter( Rating == 177.600, pred_algo =='algo1')%>%select(text)
jpg_url <- rt%>%filter( Rating == 177.600, pred_algo =='algo1')%>%select(jpg_url)
```

```{r echo=FALSE}
text
```

```{r echo=FALSE}
jpg_url <- paste( unlist(jpg_url), collapse='')
destfile <- paste("E:/NanoDegree/Wrangling/Projet/","popu.jpg",sep="")

download.file(jpg_url, destfile , mode="wb")

```


```{r echo=FALSE}
jj <- readJPEG('HR.jpg',native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)
```



<span style="color:blue">Question: </span>  How is the distribution of favorite_count and retweet_count variables?

```{r echo=FALSE}
ggplot(aes(x = favorite_count ),  data = rt%>%filter(pred_algo =='algo1'))+
  geom_histogram( binwidth = 1000, color="steelblue", fill="white")+
  scale_x_continuous(breaks = seq(0,50000,5000),limits = c(0,50000))
```



```{r echo=FALSE}
ggplot(aes(x = retweet_count ),  data = rt%>%filter(pred_algo =='algo1'))+
  geom_histogram( binwidth = 500, color="steelblue", fill="white")+
  scale_x_continuous(breaks = seq(0,30000,2000),limits = c(0,30000))
```



Tweets are more favorited thant retweeted.


<span style="color:blue">Question: </span>  How is the distribution of dog rating values.

```{r echo=FALSE}
ggplot( aes(x = Rating),  data = rt%>%filter(pred_algo =='algo1'))+
  geom_histogram( binwidth = 0.05,  color="steelblue", fill="white")+
  scale_x_continuous(breaks = seq(0,5,0.2), limits = c(0,3.5))

```


Almost normal distribution


```{r echo=FALSE}
ggplot( aes(x = " ", y = Rating),  data = rt%>%filter(pred_algo =='algo1'))+
  geom_boxplot( color="steelblue", fill="white")+
  scale_y_log10()+
    theme(aspect.ratio = 1/1)
```


Many outliers. Median Rating values is just over 1 (boxplot) and mean is around 1 also (histogram). 





<span style="color:blue">Question: </span> 
Each dog image in the WeRateDogs tweet dataset is passed to 3 different pattern recognition algorithms. Let's know how each algorithm was accurate


```{r echo=FALSE}
ggplot( aes(x = is_a_dog, fill = pred_algo), data = rt)+
  geom_bar(position = "dodge2")+
  scale_fill_brewer(palette="Dark2")+
  theme(aspect.ratio = 1/1)
```


algo2 is the most accurate algorithm.




<span style="color:blue">Question: </span>  What were the dog stages?


```{r echo=FALSE}
ggplot( aes(x = stage ),  data = rt%>%filter(pred_algo =='algo1'))+
  geom_bar(color="steelblue", fill="white")+
  theme(aspect.ratio = 1/1)
```


Most dogs are not given a satge.



# Bivariate Plots Section

Let's know which dog stage has higer reating value.


```{r echo=FALSE}
ggplot( aes(x = stage, y = Rating ),  data = rt%>%filter(pred_algo =='algo1'))+
  geom_point( position = "jitter", alpha =0.4)+
  scale_y_continuous(limits = c(0,3.5))
```

pupper dogs has a little higher rating values represent by the outliers.




# Reference: 

[how to download and display an image from an URL in R?](https://stackoverflow.com/questions/29110903/how-to-download-and-display-an-image-from-an-url-in-r)

[Convert a list into a string (for a url)](https://stackoverflow.com/questions/30861769/convert-a-list-into-a-string)
</div>
